Synthesis of Statically Analyzable Accelerator Networks From Sequential Programs

### 2016-06-21 paper.tex
before final submission modification

\numberofauthors{0} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\begin{comment}
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Shaoyi Cheng \\%\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{EECS, University of California, Berkeley}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       %\affaddr{Wallamaloo, New Zealand}\\
       \email{sh\_cheng@berkeley.edu}
% 2nd. author
\alignauthor
John Wawrzynek \\%\titlenote{The secretary disavows any knowledge of this author's actions.}\\ 
       \affaddr{EECS, University of California, Berkeley}\\
       %\affaddr{P.O. Box 1212}\\
       %\affaddr{Dublin, Ohio 43017-6221}\\
       \email{johnw@eecs.berkeley.edu}
% 3rd. author
}
\end{comment}
\maketitle
\begin{abstract}
This paper describes a general framework for
transforming a sequential program into a network of processes, which are then
converted to hardware accelerators through high level synthesis.
Also proposed is a complementing technique for performing static deadlock analysis of the generated accelerator network.
The interactions between the accelerators' schedules, the capacity of the communication
channels in the network and the memory access mechanisms are all incorporated
into our model, such that potential artificial deadlocks can be detected and resolved \textit{a priori}.

@@

Another necessary deviation from the ideal PN model lies in the capacity of the channels.
In any practical implementations of process networks, the FIFOs cannot be unbounded.
Consequently, in cases with circular dependencies, when buffers fill up writes may block and deadlocks can occur. 
These are so-called artificial deadlocks, as their occurrence is introduced by the nonideality of the implementation. % and the circular dependency formed %in these deadlocks always contain operations writing to a full FIFO.
%Note the memory ``process", which does not block on reads,
%can block on writes (responses to other processes), when a large amount of data returned are not consumed promptly. It may therefore also contribute to the development of artificial deadlocks. 
In a process network, % generated from a sequential program, 
these deadlocks, if left unresolved, would cause a mismatch between
the resultant behavior of the original code and the network. To tackle this problem, many approaches were proposed over the years, most of which involves monitoring execution and dynamically incrementing FIFO sizes when deadlock occurs~\cite{parks1995bounded}\cite{Geilen:2003:REK:1765712.1765736}\cite{4217338},
or only targets highly regular kernels.
%This is due to the infeasibility of analyzing deadlock for generic process networks at compile time. 
In our flow, we ensure, by construction, each FIFO is only read/written by a single instruction in each process, which makes the generated PN easier to analyze than a generic PN. We can therefore use a static analysis framework to find the needed FIFO sizes.

@@

\begin{algorithm}[t]
  \caption{Instruction Partitioning}\label{algo1}
  \begin{algorithmic}[1]
  \Procedure{PartitionInstNodes}{G}%\Comment{G: CDFG of loop nests}
    \State SCCs $\gets$ allStronglyConnComps(G)
  \State DAG $\gets$ collapse(SCCs,G)
  \State topoSortedNodes $\gets$ topologicalSort(DAG)
  \State longSCCs $\gets$ getSCCWithLongOp(SCCs)
  \State memNodes $\gets$ findLdStNodes(G)
  \State memLongSCC $\gets$ LongSCCs $\cup$ memNodes
  \State allSets $\gets \{\}$
  \State curSet $\gets \{\}$

@@

\begin{table}[htbp]
\caption{Benchmark Descriptions}
%\vspace{-1.2em}
\scriptsize
\centering
\begin{tabular}{| c | c | c | }
  \hline

@@

\end{tabular}
\vspace{-2.0em}
\label{tab:datasize}
\end{table}

>>>>

\numberofauthors{2} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Shaoyi Cheng \\%\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{EECS, University of California, Berkeley}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       %\affaddr{Wallamaloo, New Zealand}\\
       \email{sh\_cheng@berkeley.edu}
% 2nd. author
\alignauthor
John Wawrzynek \\%\titlenote{The secretary disavows any knowledge of this author's actions.}\\ 
       \affaddr{EECS, University of California, Berkeley}\\
       %\affaddr{P.O. Box 1212}\\
       %\affaddr{Dublin, Ohio 43017-6221}\\
       \email{johnw@eecs.berkeley.edu}
% 3rd. author
}

\maketitle
\begin{abstract}
This paper describes a general framework for
transforming a sequential program into a network of processes, which are then
converted to hardware accelerators through high level synthesis.
Also proposed is a complementing technique for performing static deadlock analysis of the generated accelerator network.
The interactions between the accelerators' schedules, the capacity of the communication
channels in the network and the memory access mechanisms are all incorporated
into our model, such that potential artificial deadlocks can be detected and resolved \textit{a priori}.

@@

Another necessary deviation from the ideal PN model lies in the capacity of the channels.
In any practical implementations of process networks, the FIFOs cannot be unbounded.
Consequently, in cases with circular dependencies, when buffers fill up writes may block and deadlocks can occur. 
These are so-called artificial deadlocks, as their occurrence is introduced by the nonideality of the implementation. % and the circular dependency formed %in these deadlocks always contain operations writing to a full FIFO.
%Note the memory ``process", which does not block on reads,
%can block on writes (responses to other processes), when a large amount of data returned are not consumed promptly. It may therefore also contribute to the development of artificial deadlocks. 
In a process network, % generated from a sequential program, 
these deadlocks, if left unresolved, would cause a mismatch between
the resultant behavior of the original code and the network. To tackle this problem, many approaches were proposed over the years, most of which involve monitoring execution and dynamically incrementing FIFO sizes when deadlock occurs~\cite{parks1995bounded}\cite{Geilen:2003:REK:1765712.1765736}\cite{4217338},
or only target highly regular kernels.
%This is due to the infeasibility of analyzing deadlock for generic process networks at compile time. 
In our flow, we ensure, by construction, each FIFO is only read/written by a single instruction in each process, which makes the generated PN easier to analyze than a generic PN. We can therefore use a static analysis framework to find the needed FIFO sizes.

@@

\setlength{\textfloatsep}{2pt}
\begin{algorithm}[t]
  \caption{Instruction Partitioning}\label{algo1}
  \begin{algorithmic}[1]
  \Procedure{PartitionInstNodes}{G}%\Comment{G: CDFG of loop nests}
    \State SCCs $\gets$ allStronglyConnComps(G)
  \State DAG $\gets$ collapse(SCCs,G)
  \State topoSortedNodes $\gets$ topologicalSort(DAG)
  \State longSCCs $\gets$ getSCCWithLongOp(SCCs)
  \State memNodes $\gets$ findLdStNodes(G)
  \State memLongSCC $\gets$ LongSCCs $\cup$ memNodes
  \State allSets $\gets \{\}$
  \State curSet $\gets \{\}$

@@

\begin{table}[htbp]
\vspace{-2.0em}
\caption{Benchmark Descriptions}
%\vspace{-1.2em}
\scriptsize
\centering
\begin{tabular}{| c | c | c | }
  \hline

@@

\end{tabular}
\vspace{-0.5em}
\label{tab:datasize}
\end{table}
